\section*{Publication}
\indent

% * Corresponding
% , $\dagger$ Equal Contribution

\cvsubsection{Refereed Journal Articles}

\begin{enumerate}[resume]
    \item \textbf{Xovee Xu}, Fan Zhou*, Kunpeng Zhang, and Siyuan Liu. 2022. CCGL: Contrastive Cascade Graph Learning. \textit{IEEE Transactions on Knowledge and Data Engineering (TKDE)}, 15 pages, 2022, Accepted.
    \item \textbf{Xovee Xu}, Ting Zhong, Ce Li, Goce Trajcevski, and Fan Zhou*. 2021. Heterogeneous dynamical academic network for learning scientific impact propagation. \textit{Knowledge-Based Systems}, vol. 238, pp. 107839, Feb 2022.
    \item Fan Zhou, Pengyu Wang, \textbf{Xovee Xu}*, Wenxin Tai, and Goce Trajcevski. 2022. Contrastive trajectory learning for tour recommendation. \textit{ACM Transactions on Intelligent Systems and Technology (TIST)}, vol. 13, no. 1, article 4, 25 pages, Feb 2022. Special Issue on Intelligent Trajectory Data Analytics.
    \item \textbf{Xovee Xu}, Fan Zhou*, Kunpeng Zhang, Siyuan Liu, and Goce Trajcevski. 2021. CasFlow: Exploring hierarchical structures and propagation uncertainty for cascade prediction. \textit{IEEE Transactions on Knowledge and Data Engineering (TKDE)}, 14 pages, Nov 2021, Early-Access.
    \item Fan Zhou, \textbf{Xovee Xu}*, Goce Trajcevski, Kunpeng Zhang. 2021. A survey of information cascade analysis: Models, predictions, and recent advances. \textit{ACM Computing Surveys (CSUR)}, vol. 54, no. 2, article 27, 36 pages, Mar 2021. 
\end{enumerate}

\cvsubsection{Refereed Conference Articles}

\begin{enumerate}[resume]
    \item Ting Zhong, Haoyang Yu, Rongfan Li, \textbf{Xovee Xu}*, Xucheng Luo, and Fan Zhou. 2022. Probabilistic Fine-Grained Urban Flow Inference With Normalizing Flows. IEEE International Conference on Acoustics, Speech, and Signal Processing (ICASSP), Singapore/Shenzhen, May 22-27, 2022, 5 pages, Accepted.
    \item Zhiyuan Wang$^\dagger$, \textbf{Xovee Xu}$^\dagger$, Goce Trajcevski, Kunpeng Zhang, Ting Zhong, and Fan Zhou*. 2022. PrEF: Probabilistic electricity forecasting via copula-augmented state space model. AAAI Conference on Artificial Intelligence (AAAI), Vancouver, Canada, Feb 22 - Mar 1, 2022, 9 pages, Accepted.
    \item Fan Zhou, Ce Li, \textbf{Xovee Xu}, Leyuan Liu*, and Goce Trajcevski. 2021. HGENA: A hyperbolic graph embedding approach for social network alignment. IEEE Global Communications Conference (GLOBECOM), Hybrid Conference (In-person/Virtual), Madrid, Spain, Dec 7-11, 2021, 6 pages.
    \item Guanyu Wang, Ting Zhong, \textbf{Xovee Xu}, Kunpeng Zhang, Fan Zhou*, and Yong Wang. 2021. Vector-quantized autoencoder with copula for collaborative filtering. ACM International Conference on Information and Knowledge Management (CIKM), Virtual Event, Nov 1-5, 2021, pp. 3458-3462.
    \item Fan Zhou, Liu Yu, \textbf{Xovee Xu}*, and Goce Trajcevski. 2021. Decoupling representation and regressor for long-tailed information cascade prediction. International ACM SIGIR Conference on Research and Development in Information Retrieval (SIGIR), Virtual Event, Jul 11-15, 2021, pp. 1875-1879.
    \item Fan Zhou, Xiuxiu \swashQ i, \textbf{Xovee Xu}, Jiahao Wang*, Ting Zhong, and Goce Trajcevski. 2020. Meta-learned user preference for topic participation prediction. IEEE Global Communications Conference (GLOBECOM), Virtual Conference, Dec 7-11, 2020, 6 pages.
    \item Fan Zhou, Zijing Wen, Ting Zhong*, Goce Trajcevski, \textbf{Xovee Xu}, and Leyuan Liu. 2020. Unsupervised user identity linkage via graph neural networks. IEEE Global Communications Conference (GLOBECOM), Virtual Conference, Dec 7-11, 2020, 6 pages.
    \item Fan Zhou, Xin Jing, \textbf{Xovee Xu}, Ting Zhong, Goce Trajcevski, and Jin Wu*. 2020. Continual information cascade learning. IEEE Global Communications Conference (GLOBECOM), Virtual Conference, Dec 7-11, 2020, 6 pages.
    \item Fan Zhou, \textbf{Xovee Xu}, Kunpeng Zhang, Goce Trajcevski, and Ting Zhong*. 2020. Variational information diffusion for probabilistic cascade prediction. IEEE International Conference on Computer Communications (INFOCOM), Virtual Conference, Jul 6-9, 2020, pp. 1618-1627.
    \newline \textbf{\color{red}INFOCOM 2020 Student Conference Award}
\end{enumerate}

\cvsubsection{Posters \& Abstracts}

\begin{enumerate}[resume]
    \item Liu Yu, \textbf{Xovee Xu}, Ting Zhong, Goce Trajcevski, and Fan Zhou. 2022. Linking Transformer to Hawkes process for information cascade prediction (Student abstact). AAAI Conference on Artificial Intelligence (AAAI), Vancouver, Canada, Feb 22 - Mar 1, 2022, 2 pages, Accepted
    \item Guanyu Wang, \textbf{Xovee Xu}, Ting Zhong, and Fan Zhou. 2022. Conditional collaborative filtering process for top-k recommender system (Student abstract). AAAI Conference on Artificial Intelligence (AAAI), Vancouver, Canada, Feb 22 - Mar 1, 2022, 2 pages, Accepted
    \item Haoyang Yu, \textbf{Xovee Xu}, Ting Zhong, and Fan Zhou. 2022. Fine-grained urban flow inference via normalizing flows (Student abstract). AAAI Conference on Artificial Intelligence (AAAI), Vancouver, Canada, Feb 22 - Mar 1, 2022, 2 pages, Accepted\newline Selected (20/111) for Three-Minute Presentation Contest
\end{enumerate}

\cvsubsection{Pre-print}

\begin{enumerate}[resume]
    \item Fan Zhou, \textbf{Xovee Xu}, Ce Li, Goce Trajcevski, Ting Zhong, and Kunpeng Zhang. 2020. A heterogeneous dynamical graph neural networks approach to quantify scientific impact. arXiv:2003.12042, Mar 2020, 8 pages. 
\end{enumerate}

% \cvsubsection{Work in Progress}

% \begin{enumerate}[resume]
%     \item Fan Zhou, Zhangtao Cheng, \textbf{Xovee Xu}, Ting Zhong, and Goce Trajcevski. 2021. Probabilistic modelling of irregularly sampled information cascade with evolution uncertainty. Under review, 2021.
%     \item Liu Yu$^\dagger$, \textbf{Xovee Xu}$^\dagger$, Ting Zhong, Goce Trajcevski, and Fan Zhou*. 2021. Transformer-enhanced Hawkes process for information cascade prediction. Under review, 2021.
%     \item \textbf{Xovee Xu}, Ting Zhong, Fan Zhou*, and Goce Trajcevski. 2022. Spatial-temporal contrasting for fine-grained urban flow inference. Under review, 2022.
% \end{enumerate}

\cvsubsection{Thesis}

\begin{enumerate}
    \item Xovee Xu. 2021. A research of information diffusion models and popularity prediction using graph neural networks (in Chinese). Master's Thesis. School of Information and Software Engineering, University of Electronic Science and Technology of China (UESTC), Chengdu, Sichuan, China, Jun 2021, 93 pages. Supervisors: Ting Zhong. Committee chair: Jingye Cai. \newline
    \textbf{\color{red}Excellent Master Thesis of UESTC (105/4929)}
\end{enumerate}

% patent
\section*{Patent}

\begin{enumerate}
    \item Fan Zhou, Chengtai Cao, Ting Zhong, and \textbf{Xovee Xu}. 2021. Training data generation method based on meta-learner and causal effect heterogeneous reaction difference estimation method (in Chinese). China Invention Patent Application, No. CN113095440A, Filed Apr 30, 2021, Published Jul 9, 2021. 
\end{enumerate}
